\documentclass[margin,line]{resume}

\begin{document}
\name{\Large Juan Batiz-Benet
  \hspace{0.20in}
  \small scientist, systems engineer, entrepreneur, student
  \hspace{0.20in}
  \normalsize jbenet@cs.stanford.edu
}
\begin{resume}


    % Purpose
    \section{\mysidestyle Purpose}
    \textbf{To further scientific and humanist progress!}


    % Education
    \section{\mysidestyle Education}

    \textbf{Stanford University} \vspace{2mm}\\\vspace{1mm}%
    \textsl{M.S. in Computer Science (Systems)}  \hfill \emph{Advisors}: Mehran Sahami, David Cheriton\\
    \textsl{B.S. in Computer Science (Systems)}  \hfill \emph{Advisors}: Philip Levis, Jerry Cain

    \section{\mysidestyle Relevant \\ Coursework}
    \begin{tabular}{llll}
cs140  & Operating Systems (+TA) \hspace{0.15\textwidth}
                             &  cs240  & Advanced Operating Systems \\
cs142  & Web Security        &  cs193p & iPhone programming     \\
cs143  & Compilers           &  cs199  & Independent Research    \\
cs144  & Networks (+TA)      &  cs221  & Artificial Intelligence \\
cs145  & Databases           &  cs229  & Machine Learning        \\
cs148  & Graphics            &  cs248  & Interactive Graphics  \\
cs161  & Algorithms          &  cs249\{a,b\} & Object Oriented Programming \\
cs109  & Probability         &  cs244b & Distributed Systems    \\
    \end{tabular}


    % Honours and Awards
    % \section{\mysidestyle Honours and\\Awards}
    %
    % Best Paper Award, Griffith School of Engineering Research Conference, Nathan, 2007              \vspace{1mm}\\%



 % Publications
 %    \section{\mysidestyle Selected Publications}
 %
 %     Paliwal, K.K., Shannon, B.J., Lyons, J.G. and K.K. W\'ojcicki,
 %     ``Speech-signal-based frequency warping'',
 %     \textsl{IEEE Signal Process. Lett.}, Vol. 16, No. 4, pp. 319-322, 2009.
 %
 % \vspace{-2mm}

    % Professional Experience
    %%%%%%%%%%%%%%%%%%%%%%%%%

    \section{\mysidestyle Industry}

    \textbf{KnowledgeTree}, internet startup.
        \textsl{Founder}
        \hfill \textbf{Dec 2012 -- Present}\\
    Empowering \textsl{anyone} to learn \textsl{everything}.

    \textbf{StartX}, startup accelerator.
        \textsl{Entrepreneur In Residence}
        \hfill \textbf{Sep 2010 -- Present}\\
    Advise and support tech startups in the program.

    \textbf{Loki Studios}, seed-funded gaming startup.
        \textsl{CTO, Co-founder}
        \hfill \textbf{May 2010 -- Dec 2012}\\
    Designing, engineering, publishing, and maintaining location based
    multiplayer mobile games.

    \textbf{Cooliris}, KPCB-funded startup.
          \textsl{Software Engineering Intern}
          \hfill \textbf{Feb 2008 -- Sep 2008}\\
    Internal web framework development, large-traffic website maintenance,
    and statistics gathering.

    \textbf{Verve Wireless}, Mobile news startup.
      \textsl{Software Engineering Intern}
      \hfill \textbf{Summer 2007}\\
    Worked as one of the four full time developers on a java web application.

    \textbf{Anticancer, Inc}, Biotech.
      \textsl{Research Intern}
      \hfill \textbf{Summer 2006}\\
    Designed and carried out own experiments for a cancer tumor targeting
    bacteria treatment.

    \section{\mysidestyle Academia}

    \textbf{Stanford University} \vspace{2mm}\\%
    \textsl{Teaching Assistant and Section Leader} \hfill \textbf{2008 -- Present}\\
    Teaching assistant for undergraduate courses in computer science, including introduction to programming methodology, operating systems, computer networks, and startups.

    \textsl{CURIS -- Phil Levis} \hfill \textbf{Summer 2009}\\
    Summer research assistant for the Stanford Information Networks Group. Worked on wireless sensor network routing protocols (CTP).

    \textsl{CURIS -- Monica Lam} \hfill \textbf{Summer 2008}\\
    Summer research assistant for the Stanford PrPl Research Group. Worked on private data sharing, and applications of the PrPl protocol.


    \section{\mysidestyle Drama}
    \textbf{\emph{wAsted}} (Director, Author) \hfill \textbf{Sep 2008 -- May 2009} \\
    Directed a company of writers and actors in devising an original full length play in response to T.S. Eliot's \emph{The Wasteland}, as part of the Drama Department's main-stage season.

    \textbf{Other Recent Credits}: \emph{Specter} (Director), \emph{Black Comedy} (Director), \emph{In Darfur} (Actor) \emph{}


    % Programming
    \section{\mysidestyle Programming Keywords}

    \textbf{Languages}: C C++ Obj-C Python PHP Javascript Java Ruby Perl Matlab Scheme ASL SQL XML\\
    \textbf{Frameworks}: Django, Smarty, CakePHP, Zend, Rails, Prototype, Scriptaculous, MooTools, Dojo \\
    \textbf{Other}: GIT SVN MVN ANT Photoshop Flash CSS Apache Tomcat Lighttpd AppEngine EC2 \\

%
% \section{\mysidestyle References}
%
% \begin{minipage}{0.4\textwidth}
%   \begin{center}
%     Phil Levis
%   \end{center}
% \end{minipage}
%
%
% \begin{minipage}{0.4\textwidth}
%   \begin{center}
%     Ross Williams
%   \end{center}
% \end{minipage}

\end{resume}
\end{document}

